---
title: "LPJml Emulator Building Tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lpjmule}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This package aims to process LPJml input and output files to create a data frame that is used for training a machine learning model that emulates LPJmL.

The functions in this package are divided into three groups:

* Processing and creating of the training data set: functions that create read and transform LPJmL binary files into a single R data frame ready to be used as input for the machine learning functions.
* Machine learning functions:
* Auxiliary and testing functions: a set of functions that test, the consistency of the results of other functions thought plots and the machine learning models, through plots and statistical analysis.

## Organizing the input folder

For this package to work, a strict organization of input files needs to be followed.
The parameter `folder` that is required by most functions need to point at folder with the following structure, for example:

* `[folder]lpjml_run_lsu_00`
  + `[file]pft.bin`
  + `[file]soilcarbon.bin`
* `[folder]lpjml_run_lsu_01`
* `[folder]lpjml_run_lsu_02`
* `[folder]lpjml_run_lsu_03`
* `[folder]lpjml_run_lsu_04`
* `[folder]lpjml_run_lsu_05`
* `[folder]lpjml_run_lsu_06`
* `[folder]lpjml_run_lsu_07`
* `[file]wet_wet_days.clm`
* `[file]tas_temperature.clm`
* `[file]soil_soil.bin`
* `[file]lwnet_longwave radiation.clm`
* `[file]rsds_shortwave radiation.clm`
* `[file]CO2_CO2 concentration.clm`
* `[file]pr_precipitation.clm`


Each folder should contain the outputs of the simulations with its respective PFT results and soil carbon concentration.
The seven lpjml input files should be stored in a parent file.

## File naming

Both input and output files will ve identified by string particles in their names, therefore, it important to add/keep string particles that identify those files correctly. As an example, the particles bellow are associated with the input files:

  ```
  temperature                   =  "tas",
  precipitation                 =  "pr",
  longwave radiation            =  "lwnet",
  shortwave radiation           =  "rsds",
  soil =                        =  "soil",
  number of wetdays             =  "wet",
  CO2 atmospheric concentration = "CO2"

  ```
As output files should be named identically between different simulations, instead of using string particles to identify them, the whole name of the file should be used when required.

## Data set info

Data set info is a list of parameters used as input for the `lpjm_inputs`, `lpjml_output` and `training_warper` functions that summarise the information needed to successfully run these two functions.
Below you find examples of how to set up `dataset_infos` to extract both harvest and soil carbon data from LPJmL binaries.

### Extracting harvest data

```{r setup}
dataset_info = list(

  #file string parts names
  temp ="tas",
  prec ="pr",
  lwnet ="lwnet",
  rsds ="rsds",
  soil ="soil",
  wet ="wet",
  co2 = "CO2",

  #Shared variables
  wyears = seq(1951,2099,10),
  cells = 67420,

  #readLPJ specific variables more information on
  #\code{\link{readLPJ}}

  file_name = "pft_harvest.pft.bin",
  crop ="mgrass",
  water = "rainfed",
  syear = 1951,
  years = 149,
  bands = 32,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE
)
```
### Extracting soil carbon data

```{r, fig.show='hold'}
dataset_info = list(

  #file string parts names
  temp ="tas",
  prec ="pr",
  lwnet ="lwnet",
  rsds ="rsds",
  soil ="soil",
  wet ="wet",
  co2 = "CO2",

  #Shared variables
  wyears = seq(1951,2099,10),
  cells = 67420,

  #readLPJ specific variables more information on
  #\code{\link{readLPJ}}

  file_name = "soilc.bin",
  crop =1,
  water =1,
  syear = 1951,
  years = 149,
  bands = 1,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE
)

```

## Usage Example

```{r eval=FALSE, warning=FALSE}
library(lpjmule)

dataset_info = list(

  #file string parts names
  temp ="tas",
  prec ="pr",
  lwnet ="lwnet",
  rsds ="rsds",
  soil ="soil",
  wet ="wet",
  co2 = "CO2",

  #Shared variables
  wyears = seq(1951,2099,10),
  cells = 67420,

  #readLPJ specific variables more information on
  #\code{\link{readLPJ}}

  file_name = "pft_harvest.pft.bin",
  crop ="mgrass",
  water = "rainfed",
  syear = 1951,
  years = 149,
  bands = 32,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE,

  #input levels should equal the levels used for each LPJml
  input_levels = c(seq(0, 2, 0.2), 2.5)
)

setwd()

training_warper("/p/projects/landuse/users/pedrosa/ML_gym/inputs/elevated",dataset_info = dataset_info)

```
