---
title: "LPJml Emulator Building Tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lpjmule}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This package aims to process LPJml input and output files to create a dataframe that is used for traininig a machine learning model that emulates LPJmL.

The functions in this package are divided in thress groups: 

* Processing and creating of the training data set: functions that create read and transforma LPJmL binary files into a single R dataframe ready to be used as input for the machine learning functions.
* Machine learning functions:
* Auxiliary and testing functions: a set of functions that test, the consistency of the results of other functions thought plots and the machine learning models, throught plots and statistical anaylsis.




## Data set info

Data set info is a list of parameters used as input for the lpjm_inputs and lpjml_output functions that sumarise the information needed to sucessfully run these two functions.
Bellow you find examples of how to set up data set infos to extracta both harvest and soil carbon data from LPJmL binaries.

### Extracting harvest data

```{r setup}
library(lpjmule)


dataset_info = list(
  
  #file string parts names
  temp ="tas", 
  prec ="pr", 
  lwnet ="lwnet", 
  rsds ="rsds", 
  soil ="soil", 
  wet ="wet", 
  co2 = "CO2",
  
  #Shared variables
  wyears = seq(1951,2099,10), 
  cells = 67420, 
  
  #readLPJ specific variables more information on 
  #\code{\link{readLPJ}}
  
  file_name = "pft_harvest.pft.bin",
  crop ="mgrass",
  water = "rainfed",
  syear = 1951,
  years = 149,
  bands = 32,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE
)
```
### Extracting soil carbon data

```{r, fig.show='hold'}


dataset_info = list(
  
  #file string parts names
  temp ="tas", 
  prec ="pr", 
  lwnet ="lwnet", 
  rsds ="rsds", 
  soil ="soil", 
  wet ="wet", 
  co2 = "CO2",
  
  #Shared variables
  wyears = seq(1951,2099,10),  
  cells = 67420, 
  
  #readLPJ specific variables more information on 
  #\code{\link{readLPJ}}
  
  file_name = "soilc.bin",
  crop =1,
  water =1,
  syear = 1951,
  years = 149,
  bands = 1,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE
)



```


