---
title: "Dataset info"
author: "Marcos Alves"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dataset info}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Data set info

Data set info is a list of parameters used as input for the lpjm_inputs and lpjml_output functions that sumarise the information needed to sucessfully run these two functions.
Bellow you find examples of how to set up data set infos to extracta both harvest and soil carbon data from LPJmL binaries.

### Extracting harvest data
```{r, fig.show='hold'}
dataset_info = list(
  
  #file string parts names
  temp ="tas", 
  prec ="pr", 
  lwnet ="lwnet", 
  rsds ="rsds", 
  soil ="soil", 
  wet ="wet", 
  co2 = "CO2",
  
  #Shared variables
  wyears = seq(1951,2099,10), 
  cells = 67420, 
  
  #readLPJ specific variables more information on 
  #\code{\link{readLPJ}}
  
  file_name = "pft_harvest.pft.bin",
  crop ="mgrass",
  water = "rainfed",
  syear = 1951,
  years = 149,
  bands = 32,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE
)
```
### Extracting soil carbon data

```{r, fig.show='hold'}


dataset_info = list(
  
  #file string parts names
  temp ="tas", 
  prec ="pr", 
  lwnet ="lwnet", 
  rsds ="rsds", 
  soil ="soil", 
  wet ="wet", 
  co2 = "CO2",
  
  #Shared variables
  wyears = seq(1951,2100,1), 
  cells = 67420, 
  
  #readLPJ specific variables more information on 
  #\code{\link{readLPJ}}
  
  file_name = "soilc.bin",
  crop =1,
  water =1,
  syear = 1951,
  years = 149,
  bands = 1,
  soilcells = FALSE, #True (59199 cells), False (67420 cells)
  monthly = FALSE
)


```


